### 2013-11-11 regressionModelling.Rmd
Tried out the country grouping. I will leave it out from the presentation and paper, too. Edited the tables, but many issues still remains, mainly explaining the analysis and later intrepretations

```{rmultiNomSimpleMlogit, results='markup'}
library(mlogit)
dat.mlogit <- df.model[,c("poverty","edu2","incsour3","income2",
                          "past.diff","future.diff","crise")]
 dat.mlogit <- mlogit.data(dat.mlogit, shape="wide", choice="poverty")
# 
# 
# model.mlogit1 <- mlogit(poverty ~ 0 | incsour3,
#                                data = dat.mlogit, 
#                                reflevel ="Social Blame")
# model.mlogit2 <- mlogit(poverty ~ 0 | incsour3 + edu2,
#                                data = dat.mlogit, 
#                                reflevel ="Social Blame")
# model.mlogit3 <- mlogit(poverty ~ 0 | incsour3 + edu2 + 
#                                       past.diff,
#                                data = dat.mlogit, 
#                                reflevel ="Social Blame")
# model.mlogit4 <- mlogit(poverty ~ 0 | incsour3 + edu2 + 
#                                       past.diff + future.diff,
#                                data = dat.mlogit, 
#                                reflevel ="Social Blame")
model.mlogit5 <- mlogit(poverty ~ 0 | incsour3 + edu2 + 
                                      past.diff + future.diff +
                                      crise, 
                               data = dat.mlogit, 
                               reflevel ="Social Blame")

@@

```{r, eval=FALSE, echo=FALSE}

screenreg(list(model.mlogit1,model.mlogit2))

f <- coeftest(model.mlogit)
xtable(as.data.frame(f))model1 <- multinom(formula = reason ~ supu+income, data = ml.06)

summary(m)
coeftest(m)

X <- mlogit.data(ml.10, shape="wide", choice="poverty")
coeftest(mlogit(poverty ~ 0 | success,
               data = X, reflevel ="Because of injustice in our society"))
summary(mlogit(poverty ~ 0 | success,
                data = X, reflevel ="Because of injustice in our society"))

coef(mlogit(poverty ~ 0 | success,
               data = X, reflevel ="Because of injustice in our society"))

@@

```{rmultiNomMulti}

```{rmultiNomMultiOutput, results='asis'}

@@

```{rmultilevelBivarSoc}
library(lme4)
bisoc.1 <- glmer(pov.log.social ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.2 <- glmer(pov.log.social ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.3 <- glmer(pov.log.social ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.4 <- glmer(pov.log.social ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.5 <- glmer(pov.log.social ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
 bisoc.6 <- glmer(pov.log.social ~ crise+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.8 <- glmer(pov.log.social ~ uw_gini+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.9 <- glmer(pov.log.social ~ gdpchange07.10+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.10 <- glmer(pov.log.social ~ wbgi_vae+(1|cntry),
                          family = binomial(logit), data = df.model)
```

```{rmultilevelBivarSocOutputNOCI, results='asis'}

coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

library(texreg)
htmlreg(list(bisoc.1,bisoc.2,
          bisoc.3,bisoc.4,
          bisoc.5,bisoc.6,
          bisoc.8,
          bisoc.9,bisoc.10),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Bivariate social blame", caption.above=TRUE)

@@

```{rmultilevelBivarInd}
biind.1 <- glmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.2 <- glmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.3 <- glmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.4 <- glmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.5 <- glmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.6 <- glmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.8 <- glmer(pov.log.individual ~ uw_gini+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.9 <- glmer(pov.log.individual ~ gdpchange07.10+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.10 <- glmer(pov.log.individual ~ wbgi_vae+(1|cntry),
                         family = binomial(logit), data = df.model)
```

```{rmultilevelBivarIndOuputNOCI, results='asis'}
library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          biind.8,
          biind.9,biind.10),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        include.pvalues=TRUE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)
```

@@

```{rmultilevelMultiIndOutputNOCI, results='asis'}

htmlreg(list(ind.0,
       ind.1,
       ind.2,
       ind.3,
       ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        ci.test = NULL,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
          caption="Logistic multilevel random intercept model for individual blame type of explanation", 
        caption.above=TRUE)

@@

```{rrmultilevelMultivarFullOutput, results='asis', eval=TRUE}
model.names.multi.2 = c("Social blame vs. not",
                      "Individual blame vs. not",
                        "Social blame vs. Individual blame")

library(texreg)
htmlreg(list(soc.4,ind.4,socVsInc),
        naive = TRUE,
        custom.model.names = model.names.multi.2,
        custom.coef.names = coef.names.multi,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)

>>>>

```{rmultiNomSimpleMlogit, results='markup'}
library(mlogit)
dat.mlogit <- df.model[,c("poverty","edu2","incsour3","income2",
                          "past.diff","future.diff","crise")]
 dat.mlogit <- mlogit.data(dat.mlogit, shape="wide", choice="poverty")
# ------- #
model.mlogit5 <- mlogit(poverty ~ 0 | incsour3 + edu2 + 
                                      past.diff + future.diff +
                                      crise, 
                               data = dat.mlogit, 
                               reflevel ="Social Blame")

@@

@@

@@

```{rmultilevelBivarSoc}
library(lme4)
df.model$group_balinCis[df.model$cntry %in% c('Czech Republic',
                                        'Hungary','Bulgaria',
                                        'Poland','Slovakia',
                                        'Slovenia','Romania')] <- 'CEE'

df.model$group_balinCis[df.model$cntry %in% c('Armenia','Azerbaijan',
                                        'Belarus','Georgia',
                                        'Kazakhstan','Kyrgyzstan',
                                        'Moldova','Tajikistan',
                                        'Ukraine','Uzbekistan','Russia',
                                        'Estonia','Latvia','Lithuania')] <- 'CIS'
df.model$group_balinCis <- factor(df.model$group_balinCis, levels=c("CEE","CIS"))

bisoc.1 <- glmer(pov.log.social ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.2 <- glmer(pov.log.social ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.3 <- glmer(pov.log.social ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.4 <- glmer(pov.log.social ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.5 <- glmer(pov.log.social ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
 bisoc.6 <- glmer(pov.log.social ~ crise+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.8 <- glmer(pov.log.social ~ uw_gini+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.9 <- glmer(pov.log.social ~ gdpchange07.10+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.10 <- glmer(pov.log.social ~ wbgi_vae+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.11 <- glmer(pov.log.social ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.12 <- glmer(pov.log.social ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)

```{rmultilevelBivarSocOutputNOCI, results='asis'}
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance","Cgroup","CgroupMod")

library(texreg)
htmlreg(list(bisoc.1,bisoc.2,
          bisoc.3,bisoc.4,
          bisoc.5,bisoc.6,
          bisoc.8,
          bisoc.9,bisoc.10,
             bisoc.11,bisoc.12),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Bivariate social blame", caption.above=TRUE)

@@

```{rmultilevelBivarInd}
biind.1 <- glmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.2 <- glmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.3 <- glmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.4 <- glmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.5 <- glmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.6 <- glmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.8 <- glmer(pov.log.individual ~ uw_gini+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.9 <- glmer(pov.log.individual ~ gdpchange07.10+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.10 <- glmer(pov.log.individual ~ wbgi_vae+(1|cntry),
                         family = binomial(logit), data = df.model)
biind.11 <- glmer(pov.log.individual ~ group_analysis+(1|cntry),
                          family = binomial(logit), data = df.model)
bisoc.12 <- glmer(pov.log.individual ~ group_balinCis+(1|cntry),
                          family = binomial(logit), data = df.model)

```{rmultilevelBivarIndOuputNOCI, results='asis'}
library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          biind.8,
          biind.9,biind.10,
          biind.11,biind.12),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        include.pvalues=TRUE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)
```

@@

```{rmultilevelMultiIndOutputNOCI, results='asis'}
htmlreg(list(ind.0,
       ind.1,
       ind.2,
       ind.3,
       ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        ci.test = NULL,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for individual blame type of explanation", 
        caption.above=TRUE)

@@

# Tables for presentation

## Partial

```{rmultilevelMultivarSlideOutput, results='asis', eval=TRUE}
library(texreg)
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

model.names.multi.A = c("SB empty",
                      "SB individual",
                      "SB all",
                      "IB empty",
                      "IB individual",
                        "IB all")

htmlreg(list(soc.0,soc.1,soc.4,
            ind.0,ind.1,ind.4),
        custom.model.names = model.names.multi.A,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)
```

## Comparison of full models

```{rrmultilevelMultivarFullOutput, results='asis', eval=TRUE}
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

model.names.multi.2 = c("Social blame vs. not",
                      "Individual blame vs. not",
                        "Social blame vs. Individual blame")

library(texreg)
htmlreg(list(soc.4,ind.4,socVsInc),
        naive = TRUE,
        custom.model.names = model.names.multi.2,
        custom.coef.names = coef.names.multi,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)
```
